Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/paper.tex
some comments from Peng Wu

@@

@@

The meaning of this hint is that the tracer should pretend that \texttt{x} is a
constant
in the code that follows. When just running the code, the function has no
effect, as it simply returns its first argument. When tracing, some extra work
is done. Let's assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning:

@@

@@

>>>>

\cfbolz{XXX stress more that "the crux of the techniques and a significant
portion of new contributions in the paper are from how to refactoring codes to
expose likely runtime constants and pure functions"}

@@

\cfbolz{XXX more precise definition of what promote does}
\cfbolz{change the hint(x, promote=True) syntax to something more readable}

@@

The hint indicates that \texttt{x} is likely a runtime constant and the JIT
should try to perform runtime specialization on it
in the code that follows. When just running the code, the function has no
effect, as it simply returns its first argument. When tracing, some extra work
is done. Let's assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning:

@@

\cfbolz{XXX explain how value specialization on the interpreter level can lead
to type specialization on the language level}

@@

\cfbolz{XXX define the meaning of purefunction more precisely, particularly because add\_attribute has side effects, which is confusing}
